---
title: "China Wind Data"
author: "Sebastian Geis"
date: "2024-01-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE}
library(progress)
library(units)
library(rvest)
library(httr)

library(metR)
library(raster)
library(terra)
library(sf)
library(stars)
library(ggspatial)
library(gstat)

library(tidyverse)
library(lubridate)
library(vroom)
#library(furrr)
```

# Load Raster
```{r}
grid_small_final <- terra::rast("./data/grid_small_final.nc")
names(grid_small_final) <- c("wind_speed", "wind_dir")
```

# Calculations with firm data
Reading in firm data
```{r, message=FALSE}
# Reading in from files
data_firm_list <- list()

data_firm_list[[1]] <- read_csv("./data/firm data/m2000_firmcoordinates_wgs84.csv") %>%
  mutate(year = 2000)
data_firm_list[[2]] <- read_csv("./data/firm data/m2001_firmcoordinates_wgs84.csv") %>%
  mutate(year = 2001)
data_firm_list[[3]] <- read_csv("./data/firm data/m2002_firmcoordinates_wgs84.csv") %>%
  mutate(year = 2002)
data_firm_list[[4]] <- read_csv("./data/firm data/m2003_firmcoordinates_wgs84.csv") %>%
  mutate(year = 2003)
data_firm_list[[5]] <- read_csv("./data/firm data/m2004_firmcoordinates_wgs84.csv") %>%
  mutate(year = 2004)
data_firm_list[[6]] <- read_csv("./data/firm data/m2005_firmcoordinates_wgs84.csv") %>%
  mutate(year = 2005)
data_firm_list[[7]] <- read_csv("./data/firm data/m2006_firmcoordinates_wgs84.csv") %>%
  mutate(year = 2006)

data_firm_list <- data_firm_list %>%
  map(~.x %>% 
        drop_na() %>% 
        st_as_sf(coords = c("lng_wgs84", "lat_wgs84"), crs = 4326))

data_firm_list[[1]]

data_firm <- map_dfr(data_firm_list, identity) %>%
  drop_na() %>%
  st_as_sf(coords = c("lng_wgs84", "lat_wgs84"), crs = 4326)
```

Reading in pollution data
```{r}
# Create empty list
data_pollution_list <- list()

# Read in pollution data
data_pollution_list[[1]] <- terra::rast("./data//pollution data/V5GL02.HybridPM25.China.200001-200012.nc")
data_pollution_list[[2]] <- terra::rast("./data//pollution data/V5GL02.HybridPM25.China.200101-200112.nc")
data_pollution_list[[3]] <- terra::rast("./data//pollution data/V5GL02.HybridPM25.China.200201-200212.nc")
data_pollution_list[[4]] <- terra::rast("./data//pollution data/V5GL02.HybridPM25.China.200301-200312.nc")
data_pollution_list[[5]] <- terra::rast("./data//pollution data/V5GL02.HybridPM25.China.200401-200412.nc")
data_pollution_list[[6]] <- terra::rast("./data//pollution data/V5GL02.HybridPM25.China.200501-200512.nc")
data_pollution_list[[7]] <- terra::rast("./data//pollution data/V5GL02.HybridPM25.China.200601-200612.nc")

# Drop units, crop and combine with wind data
data_wind_pollution_list <- data_pollution_list %>% map(function(x) {
  terra::units(x) <- NA
  data_pollution_cropped <- terra::crop(x, grid_small_final)
  c(grid_small_final, data_pollution_cropped)
})

data_wind_pollution_list[[1]]
```

NEW: Creating a terra SpatRaster with layers for every year
```{r}
# Create empty list
data_pollution_list <- list()

# Read in pollution data
data_pollution_list[[1]] <- terra::rast("./data//pollution data/V5GL02.HybridPM25.China.200001-200012.nc")
data_pollution_list[[2]] <- terra::rast("./data//pollution data/V5GL02.HybridPM25.China.200101-200112.nc")
data_pollution_list[[3]] <- terra::rast("./data//pollution data/V5GL02.HybridPM25.China.200201-200212.nc")
data_pollution_list[[4]] <- terra::rast("./data//pollution data/V5GL02.HybridPM25.China.200301-200312.nc")
data_pollution_list[[5]] <- terra::rast("./data//pollution data/V5GL02.HybridPM25.China.200401-200412.nc")
data_pollution_list[[6]] <- terra::rast("./data//pollution data/V5GL02.HybridPM25.China.200501-200512.nc")
data_pollution_list[[7]] <- terra::rast("./data//pollution data/V5GL02.HybridPM25.China.200601-200612.nc")

# Drop units, crop and combine with wind data
data_pollution_list <- imap(data_pollution_list, function(data_pollution, index) {
  terra::units(data_pollution) <- NA
  data_pollution_cropped <- terra::crop(data_pollution, grid_small_final)
  
  year <- 2000 + (index - 1)  # Calculate the year based on the index
  names(data_pollution_cropped) <- paste0("GWRPM25_", year)
  
  return(data_pollution_cropped)
})

#data_pollution_list[[2]]

data_wind_pollution <- c(grid_small_final, rast(data_pollution_list))
data_wind_pollution
```

Extract pollution and wind data from cell for each firm
```{r}
data_firm_wind_pollution_list <- map2(data_wind_pollution_list, 
                                 data_firm_list, 
                                 function(data_wind_pollution, data_firm) {
  terra::extract(data_wind_pollution, data_firm, xy = TRUE) %>%
    cbind(firm_code = data_firm$firm_code,
          year = data_firm$year) %>%
    drop_na() %>%
    st_as_sf(coords = c("x", "y"), crs = 4326)
                                   }, .progress = TRUE)

data_firm_wind_pollution_list[[1]]
```

```{r}
# Save
write_rds(data_firm_wind_pollution, "./data/data_firm_wind_pollution.rds", compress = "gz")
# Restore
data_firm_wind_pollution <- read_rds("./data/data_firm_wind_pollution.rds")
```

> PROBLEM: All the functions below need to be adjusted to take data_wind_pollution as a list

## NEW
1. Average PM 2.5 concentration in the 9 cells surrounding a firm (the firm's cell itself + the 8 adjacent cells in all directions)
2. As 1. but the sum of concentrations (yes, the raw sum)
3. Inverse-distance-weighted PM 2.5 concentration across cells within a 45° cone originating from a firm's coordinate in downwind direction and for a range of 10km
4. As 3. but the simple sum of all these cells (yes, again the raw sum)
5. As 3, but taking prevalent wind-speeds into account: the range for which we take downwind cells into account is 10km if the windspeed in the firm's cell is below the median in the overall windspeed data, while it is 25km if the windspeed is above the median.
6. As 4, but using the windspeed-split as in 5.

### Surrounding cells average & sum
Cells have this layout, where cell 5 is the cell of the firm:
```
1 | 2 | 3
4 | 5 | 6
7 | 8 | 9
```

```{r}
data_firm_wind_pollution_surrounding <- data_firm_wind_pollution %>%
  # Find firm cell number and then row and column number
  mutate(cell_number = cellFromXY(data_wind_pollution, st_coordinates(.)),
         cell_row = rowFromCell(data_wind_pollution, cell_number),
         cell_col = colFromCell(data_wind_pollution, cell_number)) %>%
  # Extract surrounding cells values
  rowwise() %>%
  mutate(cell_1_GWRPM25 = terra::extract(data_wind_pollution, cellFromRowCol(data_wind_pollution, 
                                                                             row = cell_row - 1, 
                                                                             col = cell_col - 1))$GWRPM25,
         cell_2_GWRPM25 = terra::extract(data_wind_pollution, cellFromRowCol(data_wind_pollution, 
                                                                             row = cell_row - 1, 
                                                                             col = cell_col))$GWRPM25,
         cell_3_GWRPM25 = terra::extract(data_wind_pollution, cellFromRowCol(data_wind_pollution, 
                                                                             row = cell_row - 1, 
                                                                             col = cell_col + 1))$GWRPM25,
         cell_4_GWRPM25 = terra::extract(data_wind_pollution, cellFromRowCol(data_wind_pollution, 
                                                                             row = cell_row, 
                                                                             col = cell_col - 1))$GWRPM25,
         cell_5_GWRPM25 = terra::extract(data_wind_pollution, cellFromRowCol(data_wind_pollution, 
                                                                             row = cell_row, 
                                                                             col = cell_col))$GWRPM25,
         cell_6_GWRPM25 = terra::extract(data_wind_pollution, cellFromRowCol(data_wind_pollution, 
                                                                             row = cell_row, 
                                                                             col = cell_col + 1))$GWRPM25,
         cell_7_GWRPM25 = terra::extract(data_wind_pollution, cellFromRowCol(data_wind_pollution, 
                                                                             row = cell_row + 1, 
                                                                             col = cell_col - 1))$GWRPM25,
         cell_8_GWRPM25 = terra::extract(data_wind_pollution, cellFromRowCol(data_wind_pollution, 
                                                                             row = cell_row + 1, 
                                                                             col = cell_col))$GWRPM25,
         cell_9_GWRPM25 = terra::extract(data_wind_pollution, cellFromRowCol(data_wind_pollution, 
                                                                             row = cell_row + 1, 
                                                                             col = cell_col + 1))$GWRPM25) %>%
  # Calculating average and sum
  mutate(surrounding_GWRPM25_average = rowMeans(pick(cell_1_GWRPM25:cell_9_GWRPM25)),
         surrounding_GWRPM25_sum = rowSums(pick(cell_1_GWRPM25:cell_9_GWRPM25))) %>%
  tibble() %>%
  st_drop_geometry() %>%
  select(firm_code, year, GWRPM25_surrounding_mean = surrounding_GWRPM25_average, GWRPM25_surrounding_sum = surrounding_GWRPM25_sum)

data_firm_wind_pollution_surrounding
```

Save as RDS
```{r}
# Save
write_rds(data_firm_wind_pollution_surrounding, "./data/data_firm_wind_pollution_surrounding.rds", compress = "gz")
# Restore
data_firm_wind_pollution_surrounding <- read_rds("./data/data_firm_wind_pollution_surrounding.rds")
```

### Cone weighted average
Vectorized `cone_average_func`. This is faster but may lead to problems because of memory requirements.
```{r}
cone_func <- function(point, distance = 10000, angle, width = 45) {
  coordinates <- st_coordinates(point)
  angles <- angle - width/2 + seq(0, width, by = 2)
  angle.point <- lapply(angles, function(x) geosphere::destPoint(coordinates, b = x, d = distance))
  m <- matrix(unlist(angle.point), ncol = 2, byrow = TRUE)
  allpoints <- rbind(coordinates, m, coordinates)
  cone <- st_polygon(list(allpoints)) %>% st_sfc()
  st_crs(cone) <- st_crs(point)
  return(cone)
}

cone_average_func <- function(cone, point) {
  point_df <- tibble(geom_point = point) %>%
    mutate(ID = 1:nrow(.)) %>%
    st_as_sf()
  
  terra::extract(data_wind_pollution$GWRPM25, vect(cone), xy = TRUE, touches = TRUE, ID = TRUE) %>%
    drop_na() %>%
    left_join(point_df, by = "ID") %>%
    st_as_sf(coords = c("x", "y")) %>%
    st_set_crs(4326) %>%
    mutate(distance = st_distance(geometry, geom_point, by_element = TRUE)) %>%
    mutate(weight = drop_units(distance)^-0.5) %>%
    st_drop_geometry() %>%
    summarise(mean_GWRPM25 = weighted.mean(GWRPM25, weight), .by = ID) %>%
    pull(mean_GWRPM25)
}
```

```{r}
# Setting up batches
batch_size <- 1000
num_batches <- ceiling(nrow(data_firm_wind_pollution) / batch_size)

# Initialize an empty list to store the results
result <- list()

# Setting up progress bar
pb <- progress_bar$new(format = "(:spin) :percent [:current/:total || Time: :elapsedfull || ETA: :eta]",
                       total = num_batches,
                       clear = FALSE)

# Process each batch using a loop
for (i in 1:num_batches) {
  pb$tick()
  
  start_index <- (i - 1) * batch_size + 1
  end_index <- min(i * batch_size, nrow(data_firm_wind_pollution))
  
  batch <- data_firm_wind_pollution[start_index:end_index, ]
  
  batch_result <- batch %>%
    rowwise() %>%
    mutate(geom_cone = cone_func(point = geometry, angle = wind_dir)) %>%
    ungroup() %>%
    mutate(GWRPM25_mean = cone_average_func(cone = geom_cone, point = geometry)) %>%
    st_drop_geometry() %>%
    select(firm_code, year, GWRPM25_mean)
  
  result[[i]] <- batch_result
}

# Combine the results into a single data frame
data_firm_wind_pollution_cone_average <- map_dfr(result, identity)
```

Save to RDS file
```{r}
# Save
write_rds(data_firm_wind_pollution_cone_average, file = "./data/data_firm_wind_pollution_cone_average.rds", compress = "gz")
# Restore
data_firm_wind_pollution_cone_average <- read_rds(file = "./data/data_firm_wind_pollution_cone_average.rds")
```

### Cone sum
Creating cone sum function
```{r}
cone_sum_func <- function(cone, point) {
  point_df <- tibble(geom_point = point) %>%
    mutate(ID = 1:nrow(.)) %>%
    st_as_sf()
  
  terra::extract(data_wind_pollution$GWRPM25, vect(cone), xy = TRUE, touches = TRUE, ID = TRUE) %>%
    drop_na() %>%
    left_join(point_df, by = "ID") %>%
    summarise(mean_GWRPM25 = sum(GWRPM25), .by = ID) %>%
    pull(mean_GWRPM25)
}
```

```{r}
# Setting up batches
batch_size <- 1000
num_batches <- ceiling(nrow(data_firm_wind_pollution) / batch_size)

# Initialize an empty list to store the results
result <- list()

# Setting up progress bar
pb <- progress_bar$new(format = "(:spin) :percent [:current/:total || Time: :elapsedfull || ETA: :eta]",
                       total = num_batches,
                       clear = FALSE)

# Process each batch using a loop
for (i in 1:num_batches) {
  pb$tick()
  
  start_index <- (i - 1) * batch_size + 1
  end_index <- min(i * batch_size, nrow(data_firm_wind_pollution))
  
  batch <- data_firm_wind_pollution[start_index:end_index, ]
  
  batch_result <- batch %>%
    rowwise() %>%
    mutate(geom_cone = cone_func(point = geometry, angle = wind_dir)) %>%
    ungroup() %>%
    mutate(GWRPM25_sum = cone_sum_func(cone = geom_cone, point = geometry)) %>%
    st_drop_geometry() %>%
    select(firm_code, year, GWRPM25_sum)
  
  result[[i]] <- batch_result
}

# Combine the results into a single data frame
#data_firm_wind_pollution_cone_sum <- do.call(rbind, result)

# Combine the dataframes into a single dataframe
data_firm_wind_pollution_cone_sum <- map_dfr(result, identity)
```

Save to RDS file
```{r}
# Save
write_rds(data_firm_wind_pollution_cone_sum, file = "./data/data_firm_wind_pollution_cone_sum.rds", compress = "gz")
# Restore
data_firm_wind_pollution_cone_sum <- read_rds(file = "./data/data_firm_wind_pollution_cone_sum.rds")
```

### Cone weighted average with windspeed
Working in batches
```{r}
# Find median overall windspeed
median_wind_speed <- terra::values(data_wind_pollution$wind_speed) %>%
  median(na.rm = TRUE)

# Setting up batches
batch_size <- 1000
num_batches <- ceiling(nrow(data_firm_wind_pollution) / batch_size)

# Initialize an empty list to store the results
result <- list()

# Setting up progress bar
pb <- progress_bar$new(format = "(:spin) :percent [:current/:total || Time: :elapsedfull || ETA: :eta]",
                       total = num_batches,
                       clear = FALSE)

# Process each batch using a loop
for (i in 1:num_batches) {
  pb$tick()
  
  start_index <- (i - 1) * batch_size + 1
  end_index <- min(i * batch_size, nrow(data_firm_wind_pollution))
  
  batch <- data_firm_wind_pollution[start_index:end_index, ]
  
  batch_result <- batch %>%
    rowwise() %>%
    mutate(geom_cone = cone_func(point = geometry, angle = wind_dir, 
                                 distance = if_else(wind_speed > median_wind_speed, 25000, 10000))) %>%
    ungroup() %>%
    mutate(GWRPM25_mean = cone_average_func(cone = geom_cone, point = geometry)) %>%
    st_drop_geometry() %>%
    select(firm_code, year, GWRPM25_mean)
  
  result[[i]] <- batch_result
}

# Combine the results into a single data frame
data_firm_wind_pollution_cone_average_windspeed <- map_dfr(result, identity)
```

Saving to RDS file
```{r}
# Save
write_rds(data_firm_wind_pollution_cone_average_windspeed, file = "./data/data_firm_wind_pollution_cone_average_windspeed.rds", compress = "gz")
# Restore
data_firm_wind_pollution_cone_average_windspeed <- read_rds("./data/data_firm_wind_pollution_cone_average_windspeed.rds")
```

### Cone sum with windspeed
Working in batches of 10000
```{r}
# Find median overall windspeed
median_wind_speed <- terra::values(data_wind_pollution$wind_speed) %>%
  median(na.rm = TRUE)

# Setting up batches
batch_size <- 1000
num_batches <- ceiling(nrow(data_firm_wind_pollution) / batch_size)

# Initialize an empty list to store the results
result <- list()

# Setting up progress bar
pb <- progress_bar$new(format = "(:spin) :percent [:current/:total || Time: :elapsedfull || ETA: :eta]",
                       total = num_batches,
                       clear = FALSE)

# Process each batch using a loop
for (i in 1:num_batches) {
  pb$tick()
  
  start_index <- (i - 1) * batch_size + 1
  end_index <- min(i * batch_size, nrow(data_firm_wind_pollution))
  
  batch <- data_firm_wind_pollution[start_index:end_index, ]
  
  batch_result <- batch %>%
    rowwise() %>%
    mutate(geom_cone = cone_func(point = geometry, angle = wind_dir, 
                                 distance = if_else(wind_speed > median_wind_speed, 25000, 10000))) %>%
    ungroup() %>%
    mutate(GWRPM25_sum = cone_sum_func(cone = geom_cone, point = geometry)) %>%
    st_drop_geometry() %>%
    select(firm_code, year, GWRPM25_sum)
  
  result[[i]] <- batch_result
}

# Combine the results into a single data frame
data_firm_wind_pollution_cone_sum_windspeed <- map_dfr(result, identity)
```

Save to RDS file
```{r}
# Save
write_rds(data_firm_wind_pollution_cone_sum_windspeed, file = "./data/data_firm_wind_pollution_cone_sum_windspeed.rds", compress = "gz")
# Restore
data_firm_wind_pollution_cone_sum_windspeed <- read_rds(file = "./data/data_firm_wind_pollution_cone_sum_windspeed.rds")
```

## Combining to one object
firm_code and all pollution values 1 to 6

```{r}
# Import data from .rds files
data_firm_wind_pollution_no_geom <- read_rds("./data/data_firm_wind_pollution.rds") %>%
  st_drop_geometry() %>%
  select(firm_code, year, wind_speed, wind_dir, GWRPM25)

data_firm_wind_pollution_surrounding <- read_rds("./data/data_firm_wind_pollution_surrounding.rds")
data_firm_wind_pollution_cone_average <- read_rds("./data/data_firm_wind_pollution_cone_average.rds") %>%
  rename(GWRPM25_cone_mean = GWRPM25_mean)
data_firm_wind_pollution_cone_sum <- read_rds("./data/data_firm_wind_pollution_cone_sum.rds") %>%
  rename(GWRPM25_cone_sum = GWRPM25_sum)
data_firm_wind_pollution_cone_average_windspeed <- read_rds("./data/data_firm_wind_pollution_cone_average_windspeed.rds") %>%
  rename(GWRPM25_cone_windspeed_mean = GWRPM25_mean)
data_firm_wind_pollution_cone_sum_windspeed <- read_rds("./data/data_firm_wind_pollution_cone_sum_windspeed.rds") %>%
  rename(GWRPM25_cone_windspeed_sum = GWRPM25_sum)

# Because I dont use joins but just add the columns, the order of firm_code and year is important
identical(data_firm_wind_pollution_no_geom$firm_code, data_firm_wind_pollution_surrounding$firm_code)
identical(data_firm_wind_pollution_no_geom$firm_code, data_firm_wind_pollution_cone_average$firm_code)
identical(data_firm_wind_pollution_no_geom$firm_code, data_firm_wind_pollution_cone_sum$firm_code)
identical(data_firm_wind_pollution_no_geom$firm_code, data_firm_wind_pollution_cone_average_windspeed$firm_code)
identical(data_firm_wind_pollution_no_geom$firm_code, data_firm_wind_pollution_cone_sum_windspeed$firm_code)

# Combining all data
data_firm_wind_pollution_combined <- data_firm_wind_pollution_no_geom %>%
  mutate(GWRPM25_surrounding_mean = data_firm_wind_pollution_surrounding$GWRPM25_surrounding_mean,
         GWRPM25_surrounding_sum = data_firm_wind_pollution_surrounding$GWRPM25_surrounding_sum,
         GWRPM25_cone_mean = data_firm_wind_pollution_cone_average$GWRPM25_cone_mean,
         GWRPM25_cone_sum = data_firm_wind_pollution_cone_sum$GWRPM25_cone_sum,
         GWRPM25_cone_windspeed_mean = data_firm_wind_pollution_cone_average_windspeed$GWRPM25_cone_windspeed_mean,
         GWRPM25_cone_windspeed_sum = data_firm_wind_pollution_cone_sum_windspeed$GWRPM25_cone_windspeed_sum)

data_firm_wind_pollution_combined
```

Write combined data to .rds and .csv
```{r}
# Save
write_rds(data_firm_wind_pollution_combined, "./data/data_firm_wind_pollution_combined.rds", compress = "gz")
write_csv(data_firm_wind_pollution_combined, "./data/data_firm_wind_pollution_combined.csv.gz")

# Restore
data_firm_wind_pollution_combined <- read_rds("./data/data_firm_wind_pollution_combined.rds")
```

