---
title: "China Wind Data"
author: "Sebastian Geis"
date: "2024-01-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE}
library(progress)
library(units)

library(terra)
library(sf)

library(tidyverse)
library(lubridate)
library(vroom)
#library(furrr)
```

# Load Raster
```{r}
grid_small_final <- terra::rast("./data/grid_small_final.nc")
names(grid_small_final) <- c("wind_speed", "wind_dir")
```

# Calculations with firm data
Reading in firm data
```{r, message=FALSE}
# Reading in from files
data_firm_list <- list()

data_firm_list[[1]] <- read_csv("./data/firm data/m2000_firmcoordinates_wgs84.csv") %>%
  mutate(year = 2000)
data_firm_list[[2]] <- read_csv("./data/firm data/m2001_firmcoordinates_wgs84.csv") %>%
  mutate(year = 2001)
data_firm_list[[3]] <- read_csv("./data/firm data/m2002_firmcoordinates_wgs84.csv") %>%
  mutate(year = 2002)
data_firm_list[[4]] <- read_csv("./data/firm data/m2003_firmcoordinates_wgs84.csv") %>%
  mutate(year = 2003)
data_firm_list[[5]] <- read_csv("./data/firm data/m2004_firmcoordinates_wgs84.csv") %>%
  mutate(year = 2004)
data_firm_list[[6]] <- read_csv("./data/firm data/m2005_firmcoordinates_wgs84.csv") %>%
  mutate(year = 2005)
data_firm_list[[7]] <- read_csv("./data/firm data/m2006_firmcoordinates_wgs84.csv") %>%
  mutate(year = 2006)

# Remove NAs and add coordinates
data_firm_list <- data_firm_list %>%
  map(~.x %>% 
        drop_na() %>% 
        st_as_sf(coords = c("lng_wgs84", "lat_wgs84"), crs = 4326))

# Show first list element for year 2000
data_firm_list[[1]]
```

Reading in pollution data
```{r}
# Create empty list
data_pollution_list <- list()

# Read in pollution data
data_pollution_list[[1]] <- terra::rast("./data//pollution data/V5GL02.HybridPM25.China.200001-200012.nc")
data_pollution_list[[2]] <- terra::rast("./data//pollution data/V5GL02.HybridPM25.China.200101-200112.nc")
data_pollution_list[[3]] <- terra::rast("./data//pollution data/V5GL02.HybridPM25.China.200201-200212.nc")
data_pollution_list[[4]] <- terra::rast("./data//pollution data/V5GL02.HybridPM25.China.200301-200312.nc")
data_pollution_list[[5]] <- terra::rast("./data//pollution data/V5GL02.HybridPM25.China.200401-200412.nc")
data_pollution_list[[6]] <- terra::rast("./data//pollution data/V5GL02.HybridPM25.China.200501-200512.nc")
data_pollution_list[[7]] <- terra::rast("./data//pollution data/V5GL02.HybridPM25.China.200601-200612.nc")

# Drop units, crop and combine with wind data
data_wind_pollution_list <- data_pollution_list %>% map(function(x) {
  terra::units(x) <- NA
  data_pollution_cropped <- terra::crop(x, grid_small_final)
  c(grid_small_final, data_pollution_cropped)
})

# Show first list element for year 2000
data_wind_pollution_list[[1]]
```

Extract pollution and wind data from cell for each firm
```{r}
data_firm_wind_pollution_list <- map2(data_wind_pollution_list,
                                      data_firm_list,
                                      function(data_wind_pollution, data_firm) {
                                        terra::extract(data_wind_pollution, data_firm, xy = TRUE) %>%
                                          cbind(firm_code = data_firm$firm_code,
                                                year = data_firm$year) %>%
                                          drop_na() %>%
                                          st_as_sf(coords = c("x", "y"), crs = 4326)
                                      }, .progress = TRUE)

data_firm_wind_pollution_list[[1]]
```

# Calculations
1. Average PM 2.5 concentration in the 9 cells surrounding a firm (the firm's cell itself + the 8 adjacent cells in all directions)
2. As 1. but the sum of concentrations (yes, the raw sum)
3. Inverse-distance-weighted PM 2.5 concentration across cells within a 45° cone originating from a firm's coordinate in downwind direction and for a range of 10km
4. As 3. but the simple sum of all these cells (yes, again the raw sum)
5. As 3, but taking prevalent wind-speeds into account: the range for which we take downwind cells into account is 10km if the windspeed in the firm's cell is below the median in the overall windspeed data, while it is 25km if the windspeed is above the median.
6. As 4, but using the windspeed-split as in 5.

Creating functions
```{r}
# Function to create cone geometry
cone_func <- function(point, distance = 10000, angle, width = 45) {
  coordinates <- st_coordinates(point)
  angles <- angle - width/2 + seq(0, width, by = 2)
  angle.point <- lapply(angles, function(x) geosphere::destPoint(coordinates, b = x, d = distance))
  m <- matrix(unlist(angle.point), ncol = 2, byrow = TRUE)
  allpoints <- rbind(coordinates, m, coordinates)
  cone <- st_polygon(list(allpoints)) %>% st_sfc()
  st_crs(cone) <- st_crs(point)
  return(cone)
}

# Function that calculates the extracts the grid values from the cone geometry
# and calculates the weighted average
cone_average_func <- function(cone, point, raster) {
  point_df <- tibble(geom_point = point) %>%
    mutate(ID = 1:nrow(.)) %>%
    st_as_sf()
  
  terra::extract(raster$GWRPM25, vect(cone), xy = TRUE, touches = TRUE, ID = TRUE) %>%
    drop_na() %>%
    left_join(point_df, by = "ID") %>%
    st_as_sf(coords = c("x", "y")) %>%
    st_set_crs(4326) %>%
    mutate(distance = st_distance(geometry, geom_point, by_element = TRUE)) %>%
    mutate(weight = drop_units(distance)^-0.5) %>%
    st_drop_geometry() %>%
    summarise(mean_GWRPM25 = weighted.mean(GWRPM25, weight), .by = ID) %>%
    pull(mean_GWRPM25)
}

# Function that calculates the extracts the grid values from the cone geometry
# and calculates the sum
cone_sum_func <- function(cone, point, raster) {
  point_df <- tibble(geom_point = point) %>%
    mutate(ID = 1:nrow(.)) %>%
    st_as_sf()
  
  terra::extract(raster$GWRPM25, vect(cone), xy = TRUE, touches = TRUE, ID = TRUE) %>%
    drop_na() %>%
    left_join(point_df, by = "ID") %>%
    summarise(mean_GWRPM25 = sum(GWRPM25), .by = ID) %>%
    pull(mean_GWRPM25)
}
```

## Surrounding cells average & sum
Cells have this layout, where cell 5 is the cell of the firm:
```
1 | 2 | 3
4 | 5 | 6
7 | 8 | 9
```

Calculations
```{r}
f <- function(data_wind_pollution, data_firm_wind_pollution) {
  data_firm_wind_pollution %>%
    # Find firm cell number and then row and column number
    mutate(
      cell_number = cellFromXY(data_wind_pollution, st_coordinates(.)),
      cell_row = rowFromCell(data_wind_pollution, cell_number),
      cell_col = colFromCell(data_wind_pollution, cell_number)
    ) %>%
    # Extract surrounding cells values
    rowwise() %>%
    mutate(
      cell_1_GWRPM25 = terra::extract(
        data_wind_pollution,
        cellFromRowCol(data_wind_pollution,
                       row = cell_row - 1,
                       col = cell_col - 1)
      )$GWRPM25,
      cell_2_GWRPM25 = terra::extract(
        data_wind_pollution,
        cellFromRowCol(data_wind_pollution,
                       row = cell_row - 1,
                       col = cell_col)
      )$GWRPM25,
      cell_3_GWRPM25 = terra::extract(
        data_wind_pollution,
        cellFromRowCol(data_wind_pollution,
                       row = cell_row - 1,
                       col = cell_col + 1)
      )$GWRPM25,
      cell_4_GWRPM25 = terra::extract(
        data_wind_pollution,
        cellFromRowCol(data_wind_pollution,
                       row = cell_row,
                       col = cell_col - 1)
      )$GWRPM25,
      cell_5_GWRPM25 = terra::extract(
        data_wind_pollution,
        cellFromRowCol(data_wind_pollution,
                       row = cell_row,
                       col = cell_col)
      )$GWRPM25,
      cell_6_GWRPM25 = terra::extract(
        data_wind_pollution,
        cellFromRowCol(data_wind_pollution,
                       row = cell_row,
                       col = cell_col + 1)
      )$GWRPM25,
      cell_7_GWRPM25 = terra::extract(
        data_wind_pollution,
        cellFromRowCol(data_wind_pollution,
                       row = cell_row + 1,
                       col = cell_col - 1)
      )$GWRPM25,
      cell_8_GWRPM25 = terra::extract(
        data_wind_pollution,
        cellFromRowCol(data_wind_pollution,
                       row = cell_row + 1,
                       col = cell_col)
      )$GWRPM25,
      cell_9_GWRPM25 = terra::extract(
        data_wind_pollution,
        cellFromRowCol(data_wind_pollution,
                       row = cell_row + 1,
                       col = cell_col + 1)
      )$GWRPM25
    ) %>%
    # Calculating average and sum
    mutate(
      surrounding_GWRPM25_average = rowMeans(pick(cell_1_GWRPM25:cell_9_GWRPM25)),
      surrounding_GWRPM25_sum = rowSums(pick(cell_1_GWRPM25:cell_9_GWRPM25))
    ) %>%
    tibble() %>%
    st_drop_geometry() %>%
    select(
      firm_code,
      year,
      GWRPM25_surrounding_mean = surrounding_GWRPM25_average,
      GWRPM25_surrounding_sum = surrounding_GWRPM25_sum
    )
}

# Using purrr's map2() function to apply something to the first elements of both lists which contain everything from the year 2000, then move to the second elements with the year 2001 and so on...
data_firm_wind_pollution_surrounding <- map2(data_wind_pollution_list,
     data_firm_wind_pollution_list, 
     f, .progress = TRUE) %>%
  list_rbind()
```

Save as RDS
```{r}
# Save
write_rds(data_firm_wind_pollution_surrounding, "./data/data_firm_wind_pollution_surrounding.rds", compress = "gz")
# Restore
data_firm_wind_pollution_surrounding <- read_rds("./data/data_firm_wind_pollution_surrounding.rds")
```

```{r}
rm(data_firm_wind_pollution_surrounding)
```


## Cone weighted average
Calculations
```{r}
# Function that creates batches, calls cone_func() and cone_average_func()
f <- function(data_wind_pollution, data_firm_wind_pollution){
    # Setting up batches
    batch_size <- 1000
    num_batches <- ceiling(nrow(data_firm_wind_pollution) / batch_size)
    
    # Initialize an empty list to store the results
    result <- list()
    
    # Process each batch using a loop
    for (i in 1:num_batches) {
      start_index <- (i - 1) * batch_size + 1
      end_index <- min(i * batch_size, nrow(data_firm_wind_pollution))
      
      batch <- data_firm_wind_pollution[start_index:end_index, ]
      
      batch_result <- batch %>%
        rowwise() %>%
        mutate(geom_cone = cone_func(point = geometry, angle = wind_dir)) %>%
        ungroup() %>%
        # Only this part will change ---
        mutate(GWRPM25_mean = cone_average_func(cone = geom_cone, 
                                                     point = geometry,
                                                     raster = data_wind_pollution)) %>%
        # ---
        st_drop_geometry() %>%
        select(firm_code, year, GWRPM25_mean)
      
      result[[i]] <- batch_result
    }
    
    # Combine the results into a single data frame and return
    result %>%
      list_rbind()
}

# Using purrr's map2() function to apply something to the first elements of both lists which contain everything from the year 2000, then move to the second elements with the year 2001 and so on...
data_firm_wind_pollution_cone_average <- map2(data_wind_pollution_list,
     data_firm_wind_pollution_list, 
     f, .progress = TRUE) %>%
  list_rbind()
```

Save to RDS file
```{r}
# Save
write_rds(data_firm_wind_pollution_cone_average, file = "./data/data_firm_wind_pollution_cone_average.rds", compress = "gz")
# Restore
data_firm_wind_pollution_cone_average <- read_rds(file = "./data/data_firm_wind_pollution_cone_average.rds")
```

```{r}
rm(data_firm_wind_pollution_cone_average)
```


## Cone sum
Calculations
```{r}
# Function that creates batches, calls cone_func() and cone_average_func()
f <- function(data_wind_pollution, data_firm_wind_pollution){
    # Setting up batches
    batch_size <- 1000
    num_batches <- ceiling(nrow(data_firm_wind_pollution) / batch_size)
    
    # Initialize an empty list to store the results
    result <- list()
    
    # Process each batch using a loop
    for (i in 1:num_batches) {
      start_index <- (i - 1) * batch_size + 1
      end_index <- min(i * batch_size, nrow(data_firm_wind_pollution))
      
      batch <- data_firm_wind_pollution[start_index:end_index, ]
      
      batch_result <- batch %>%
        rowwise() %>%
        mutate(geom_cone = cone_func(point = geometry, angle = wind_dir)) %>%
        ungroup() %>%
        # Only this part will change ---
        mutate(GWRPM25_mean = cone_sum_func(cone = geom_cone,
                                            point = geometry,
                                            raster = data_wind_pollution)) %>%
        # ---
        st_drop_geometry() %>%
        select(firm_code, year, GWRPM25_mean)
      
      result[[i]] <- batch_result
    }
    
    # Combine the results into a single data frame and return
    result %>%
      list_rbind()
}

# Using purrr's map2() function to apply something to the first elements of both lists which contain everything from the year 2000, then move to the second elements with the year 2001 and so on...
data_firm_wind_pollution_cone_sum <- map2(data_wind_pollution_list,
     data_firm_wind_pollution_list, 
     f, .progress = TRUE) %>%
  list_rbind()
```

Save to RDS file
```{r}
# Save
write_rds(data_firm_wind_pollution_cone_sum, file = "./data/data_firm_wind_pollution_cone_sum.rds", compress = "gz")
# Restore
data_firm_wind_pollution_cone_sum <- read_rds(file = "./data/data_firm_wind_pollution_cone_sum.rds")
```

```{r}
rm(data_firm_wind_pollution_cone_sum)
```


## Cone weighted average with windspeed
Calculations
```{r}
# Function that creates batches, calls cone_func() and cone_average_func()
f <- function(data_wind_pollution, data_firm_wind_pollution){
    # Find median overall windspeed
    median_wind_speed <- terra::values(data_wind_pollution$wind_speed) %>%
      median(na.rm = TRUE)
  
    # Setting up batches
    batch_size <- 1000
    num_batches <- ceiling(nrow(data_firm_wind_pollution) / batch_size)
    
    # Initialize an empty list to store the results
    result <- list()
    
    # Process each batch using a loop
    for (i in 1:num_batches) {
      start_index <- (i - 1) * batch_size + 1
      end_index <- min(i * batch_size, nrow(data_firm_wind_pollution))
      
      batch <- data_firm_wind_pollution[start_index:end_index, ]
      
      batch_result <- batch %>%
        rowwise() %>%
        mutate(geom_cone = cone_func(point = geometry, angle = wind_dir,
                                     distance = if_else(wind_speed > median_wind_speed, 
                                                        25000, 10000))) %>%
        ungroup() %>%
        # Only this part will change ---
        mutate(GWRPM25_mean = cone_average_func(cone = geom_cone,
                                                point = geometry,
                                                raster = data_wind_pollution)) %>%
        # ---
        st_drop_geometry() %>%
        select(firm_code, year, GWRPM25_mean)
      
      result[[i]] <- batch_result
    }
    
    # Combine the results into a single data frame and return
    result %>%
      list_rbind()
}

# Using purrr's map2() function to apply something to the first elements of both lists which contain everything from the year 2000, then move to the second elements with the year 2001 and so on...
data_firm_wind_pollution_cone_average_windspeed <- map2(data_wind_pollution_list,
     data_firm_wind_pollution_list, 
     f, .progress = TRUE) %>%
  list_rbind()
```

Saving to RDS file
```{r}
# Save
write_rds(data_firm_wind_pollution_cone_average_windspeed, file = "./data/data_firm_wind_pollution_cone_average_windspeed.rds", compress = "gz")
# Restore
data_firm_wind_pollution_cone_average_windspeed <- read_rds("./data/data_firm_wind_pollution_cone_average_windspeed.rds")
```

```{r}
rm(data_firm_wind_pollution_cone_average_windspeed)
```


## Cone sum with windspeed
Calculations
```{r}
# Function that creates batches, calls cone_func() and cone_average_func()
f <- function(data_wind_pollution, data_firm_wind_pollution){
    # Find median overall windspeed
    median_wind_speed <- terra::values(data_wind_pollution$wind_speed) %>%
      median(na.rm = TRUE)
  
    # Setting up batches
    batch_size <- 1000
    num_batches <- ceiling(nrow(data_firm_wind_pollution) / batch_size)
    
    # Initialize an empty list to store the results
    result <- list()
    
    # Process each batch using a loop
    for (i in 1:num_batches) {
      start_index <- (i - 1) * batch_size + 1
      end_index <- min(i * batch_size, nrow(data_firm_wind_pollution))
      
      batch <- data_firm_wind_pollution[start_index:end_index, ]
      
      batch_result <- batch %>%
        rowwise() %>%
        mutate(geom_cone = cone_func(point = geometry, angle = wind_dir,
                                     distance = if_else(wind_speed > median_wind_speed, 
                                                        25000, 10000))) %>%
        ungroup() %>%
        # Only this part will change ---
        mutate(GWRPM25_mean = cone_sum_func(cone = geom_cone,
                                            point = geometry,
                                            raster = data_wind_pollution)) %>%
        # ---
        st_drop_geometry() %>%
        select(firm_code, year, GWRPM25_mean)
      
      result[[i]] <- batch_result
    }
    
    # Combine the results into a single data frame and return
    result %>%
      list_rbind()
}

# Using purrr's map2() function to apply something to the first elements of both lists which contain everything from the year 2000, then move to the second elements with the year 2001 and so on...
data_firm_wind_pollution_cone_average_windspeed <- map2(data_wind_pollution_list,
     data_firm_wind_pollution_list_test, 
     f, .progress = TRUE) %>%
  list_rbind()
```

Save to RDS file
```{r}
# Save
write_rds(data_firm_wind_pollution_cone_sum_windspeed, file = "./data/data_firm_wind_pollution_cone_sum_windspeed.rds", compress = "gz")
# Restore
data_firm_wind_pollution_cone_sum_windspeed <- read_rds(file = "./data/data_firm_wind_pollution_cone_sum_windspeed.rds")
```

```{r}
rm(data_firm_wind_pollution_cone_sum_windspeed)
```


# Combining to one object
firm_code and all pollution values 1 to 6

```{r}
# Import data from .rds files
data_firm_wind_pollution_no_geom <- read_rds("./data/data_firm_wind_pollution.rds") %>%
  st_drop_geometry() %>%
  select(firm_code, year, wind_speed, wind_dir, GWRPM25)

data_firm_wind_pollution_surrounding <- read_rds("./data/data_firm_wind_pollution_surrounding.rds")
data_firm_wind_pollution_cone_average <- read_rds("./data/data_firm_wind_pollution_cone_average.rds") %>%
  rename(GWRPM25_cone_mean = GWRPM25_mean)
data_firm_wind_pollution_cone_sum <- read_rds("./data/data_firm_wind_pollution_cone_sum.rds") %>%
  rename(GWRPM25_cone_sum = GWRPM25_sum)
data_firm_wind_pollution_cone_average_windspeed <- read_rds("./data/data_firm_wind_pollution_cone_average_windspeed.rds") %>%
  rename(GWRPM25_cone_windspeed_mean = GWRPM25_mean)
data_firm_wind_pollution_cone_sum_windspeed <- read_rds("./data/data_firm_wind_pollution_cone_sum_windspeed.rds") %>%
  rename(GWRPM25_cone_windspeed_sum = GWRPM25_sum)

# Because I dont use joins but just add the columns, the order of firm_code and year is important
identical(data_firm_wind_pollution_no_geom$firm_code, data_firm_wind_pollution_surrounding$firm_code)
identical(data_firm_wind_pollution_no_geom$firm_code, data_firm_wind_pollution_cone_average$firm_code)
identical(data_firm_wind_pollution_no_geom$firm_code, data_firm_wind_pollution_cone_sum$firm_code)
identical(data_firm_wind_pollution_no_geom$firm_code, data_firm_wind_pollution_cone_average_windspeed$firm_code)
identical(data_firm_wind_pollution_no_geom$firm_code, data_firm_wind_pollution_cone_sum_windspeed$firm_code)

# Combining all data
data_firm_wind_pollution_combined <- data_firm_wind_pollution_no_geom %>%
  mutate(GWRPM25_surrounding_mean = data_firm_wind_pollution_surrounding$GWRPM25_surrounding_mean,
         GWRPM25_surrounding_sum = data_firm_wind_pollution_surrounding$GWRPM25_surrounding_sum,
         GWRPM25_cone_mean = data_firm_wind_pollution_cone_average$GWRPM25_cone_mean,
         GWRPM25_cone_sum = data_firm_wind_pollution_cone_sum$GWRPM25_cone_sum,
         GWRPM25_cone_windspeed_mean = data_firm_wind_pollution_cone_average_windspeed$GWRPM25_cone_windspeed_mean,
         GWRPM25_cone_windspeed_sum = data_firm_wind_pollution_cone_sum_windspeed$GWRPM25_cone_windspeed_sum)

data_firm_wind_pollution_combined
```

Write combined data to .rds and .csv
```{r}
# Save
write_rds(data_firm_wind_pollution_combined, "./data/data_firm_wind_pollution_combined.rds", compress = "gz")
write_csv(data_firm_wind_pollution_combined, "./data/data_firm_wind_pollution_combined.csv.gz")

# Restore
data_firm_wind_pollution_combined <- read_rds("./data/data_firm_wind_pollution_combined.rds")
```

