---
title: "China Wind Data"
author: "Sebastian Geis"
date: "2024-01-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE}
library(progress)
library(units)

library(terra)
library(sf)

library(tidyverse)
library(lubridate)
library(vroom)
#library(furrr)
```

# Load Raster
```{r}
grid_small_final <- terra::rast("./data/grid_small_final.nc")
names(grid_small_final) <- c("wind_speed", "wind_dir")
```

# Calculations with firm data
Reading in firm data
```{r, message=FALSE}
# Reading in from files
data_firm_list <- list()

data_firm_list[[1]] <- read_csv("./data/firm data/m2000_firmcoordinates_wgs84.csv") %>%
  mutate(year = 2000)
data_firm_list[[2]] <- read_csv("./data/firm data/m2001_firmcoordinates_wgs84.csv") %>%
  mutate(year = 2001)
data_firm_list[[3]] <- read_csv("./data/firm data/m2002_firmcoordinates_wgs84.csv") %>%
  mutate(year = 2002)
data_firm_list[[4]] <- read_csv("./data/firm data/m2003_firmcoordinates_wgs84.csv") %>%
  mutate(year = 2003)
data_firm_list[[5]] <- read_csv("./data/firm data/m2004_firmcoordinates_wgs84.csv") %>%
  mutate(year = 2004)
data_firm_list[[6]] <- read_csv("./data/firm data/m2005_firmcoordinates_wgs84.csv") %>%
  mutate(year = 2005)
data_firm_list[[7]] <- read_csv("./data/firm data/m2006_firmcoordinates_wgs84.csv") %>%
  mutate(year = 2006)

# Remove NAs and add coordinates
data_firm_list <- data_firm_list %>%
  map(~.x %>% 
        drop_na() %>% 
        st_as_sf(coords = c("lng_wgs84", "lat_wgs84"), crs = 4326))

# Show first list element for year 2000
data_firm_list[[1]]
```

Reading in pollution data
```{r}
# Create empty list
data_pollution_list <- list()

# Read in pollution data
data_pollution_list[[1]] <- terra::rast("./data//pollution data/V5GL02.HybridPM25.China.200001-200012.nc")
data_pollution_list[[2]] <- terra::rast("./data//pollution data/V5GL02.HybridPM25.China.200101-200112.nc")
data_pollution_list[[3]] <- terra::rast("./data//pollution data/V5GL02.HybridPM25.China.200201-200212.nc")
data_pollution_list[[4]] <- terra::rast("./data//pollution data/V5GL02.HybridPM25.China.200301-200312.nc")
data_pollution_list[[5]] <- terra::rast("./data//pollution data/V5GL02.HybridPM25.China.200401-200412.nc")
data_pollution_list[[6]] <- terra::rast("./data//pollution data/V5GL02.HybridPM25.China.200501-200512.nc")
data_pollution_list[[7]] <- terra::rast("./data//pollution data/V5GL02.HybridPM25.China.200601-200612.nc")

# Drop units, crop and combine with wind data
data_wind_pollution_list <- data_pollution_list %>% map(function(x) {
  terra::units(x) <- NA
  data_pollution_cropped <- terra::crop(x, grid_small_final)
  c(grid_small_final, data_pollution_cropped)
})

# Show first list element for year 2000
data_wind_pollution_list[[1]]
```

Extract pollution and wind data from cell for each firm
```{r}
data_firm_wind_pollution_list <- map2(data_wind_pollution_list,
                                      data_firm_list,
                                      function(data_wind_pollution, data_firm) {
                                        terra::extract(data_wind_pollution, data_firm, xy = TRUE) %>%
                                          cbind(firm_code = data_firm$firm_code,
                                                year = data_firm$year) %>%
                                          drop_na() %>%
                                          st_as_sf(coords = c("x", "y"), crs = 4326)
                                      }, .progress = TRUE)

rm(data_firm_list)

data_firm_wind_pollution_list[[1]]
```

# Calculations
1. Average PM 2.5 concentration in the 9 cells surrounding a firm (the firm's cell itself + the 8 adjacent cells in all directions)
2. As 1. but the sum of concentrations (yes, the raw sum)
3. Inverse-distance-weighted PM 2.5 concentration across cells within a 45° cone originating from a firm's coordinate in downwind direction and for a range of 10km
4. As 3. but the simple sum of all these cells (yes, again the raw sum)
5. As 3, but taking prevalent wind-speeds into account: the range for which we take downwind cells into account is 10km if the windspeed in the firm's cell is below the median in the overall windspeed data, while it is 25km if the windspeed is above the median.
6. As 4, but using the windspeed-split as in 5.

Creating functions
```{r}
# Function to create cone geometry
cone_func <- function(point, distance = 10000, angle, width = 45) {
  coordinates <- st_coordinates(point)
  angles <- angle - width/2 + seq(0, width, by = 2)
  angle.point <- lapply(angles, function(x) geosphere::destPoint(coordinates, b = x, d = distance))
  m <- matrix(unlist(angle.point), ncol = 2, byrow = TRUE)
  allpoints <- rbind(coordinates, m, coordinates)
  cone <- st_polygon(list(allpoints)) %>% st_sfc()
  st_crs(cone) <- st_crs(point)
  return(cone)
}

# Function that calculates the extracts the grid values from the cone geometry
# and calculates the weighted average
cone_average_func <- function(cone, point, raster) {
  point_df <- tibble(geom_point = point) %>%
    mutate(ID = 1:nrow(.)) %>%
    st_as_sf()
  
  terra::extract(raster$GWRPM25, vect(cone), xy = TRUE, touches = TRUE, ID = TRUE) %>%
    drop_na() %>%
    left_join(point_df, by = "ID") %>%
    st_as_sf(coords = c("x", "y")) %>%
    st_set_crs(4326) %>%
    mutate(distance = st_distance(geometry, geom_point, by_element = TRUE)) %>%
    mutate(weight = drop_units(distance)^-0.5) %>%
    st_drop_geometry() %>%
    summarise(mean_GWRPM25 = weighted.mean(GWRPM25, weight), .by = ID) %>%
    pull(mean_GWRPM25)
}

# Function that calculates the extracts the grid values from the cone geometry
# and calculates the sum
cone_sum_func <- function(cone, point, raster) {
  point_df <- tibble(geom_point = point) %>%
    mutate(ID = 1:nrow(.)) %>%
    st_as_sf()
  
  terra::extract(raster$GWRPM25, vect(cone), xy = TRUE, touches = TRUE, ID = TRUE) %>%
    drop_na() %>%
    left_join(point_df, by = "ID") %>%
    summarise(mean_GWRPM25 = sum(GWRPM25), .by = ID) %>%
    pull(mean_GWRPM25)
}

# Create progress bar for loops
initialize_progress_bar <- function(total) {
  progress_bar$new(
    format = "(:spin) :percent [:current/:total || Time: :elapsedfull || ETA: :eta]",
    total = total,
    clear = FALSE
  )
}
```

## Surrounding cells average & sum
Cells have this layout, where cell 5 is the cell of the firm:
```{r}
matrix(c(-1, -1, -1, 0, -1, 1, 0, -1, 0, 0, 0, 1, 1, -1, 1, 0, 1, 1), ncol = 2, byrow = TRUE)
```
On a map, this would look like this:
```
1 | 4 | 7
2 | 5 | 8
3 | 6 | 9
```

Calculations
```{r}
# Process batch
process_batch <- function(data_wind_pollution, data_firm_wind_pollution) {
  # Extract cell numbers, rows, and columns
  data_firm_wind_pollution <- data_firm_wind_pollution %>%
    mutate(
      cell_number = cellFromXY(data_wind_pollution, st_coordinates(.)),
      cell_row = rowFromCell(data_wind_pollution, cell_number),
      cell_col = colFromCell(data_wind_pollution, cell_number)
    )
  
  # Create a matrix of row and column offsets
  offsets <- matrix(c(-1, -1, -1, 0, -1, 1, 0, -1, 0, 0, 0, 1, 1, -1, 1, 0, 1, 1), ncol = 2, byrow = TRUE)
  
  # Extract surrounding cell values using matrix operations
  surrounding_cells <- data_firm_wind_pollution %>%
    mutate(cell_values = map2(cell_row, cell_col, function(row, col) {
      cells <- cbind(row + offsets[,1], col + offsets[,2])
      terra::extract(data_wind_pollution, cellFromRowCol(data_wind_pollution, cells[,1], cells[,2]))$GWRPM25
    }))
  
  # Calculate average and sum
  data_firm_wind_pollution <- surrounding_cells %>%
    mutate(
      surrounding_GWRPM25_average = map_dbl(cell_values, mean),
      surrounding_GWRPM25_sum = map_dbl(cell_values, sum)
    ) %>%
    st_drop_geometry() %>%
    select(
      firm_code,
      year,
      GWRPM25_surrounding_mean = surrounding_GWRPM25_average,
      GWRPM25_surrounding_sum = surrounding_GWRPM25_sum
    )
  
  return(data_firm_wind_pollution)
}

# Define the batch size
batch_size <- 1000

# Initialize progress bar
total_batches <- sum(map_dbl(data_firm_wind_pollution_list, nrow)) / batch_size
pb <- initialize_progress_bar(total_batches)

# Initialize an empty list to store the results
results <- list()
counter <- 1

# Loop over the indices of the elements in the list
for (element in seq_along(data_wind_pollution_list)) {
  # Extract the corresponding elements from each list
  data_wind_pollution <- data_wind_pollution_list[[element]]
  data_firm_wind_pollution <- data_firm_wind_pollution_list[[element]]
  
  # Calculate the number of batches
  num_batches <- ceiling(nrow(data_firm_wind_pollution) / batch_size)
  
  # Process each batch
  for (i in 1:num_batches) {
    pb$tick()
    
    # Define row indices for the current batch
    start_index <- (i - 1) * batch_size + 1
    end_index <- min(i * batch_size, nrow(data_firm_wind_pollution))
    
    # Extract the batch
    batch_data <- data_firm_wind_pollution[start_index:end_index, ]
    
    # Apply the function f to the batch
    batch_result <- process_batch(data_wind_pollution, batch_data)
    
    # Store the result in the results list
    results[[counter]] <- batch_result
    counter <- counter + 1
  }
}

# Combine all results into a single data frame
data_firm_wind_pollution_surrounding <- results %>% list_rbind()
```

Save as RDS
```{r}
# Save
write_rds(data_firm_wind_pollution_surrounding, "./data/data_firm_wind_pollution_surrounding.rds", compress = "gz")
# Restore
data_firm_wind_pollution_surrounding <- read_rds("./data/data_firm_wind_pollution_surrounding.rds")
```

```{r}
rm(data_firm_wind_pollution_surrounding)
```


## Cone weighted average
Calculations
```{r}
# Create function
process_batch <- function(batch_data, wind_pollution_data) {
  batch_data %>%
    rowwise() %>%
    mutate(geom_cone = cone_func(point = geometry, angle = wind_dir)) %>%
    ungroup() %>%
    mutate(GWRPM25_mean = cone_average_func(cone = geom_cone, 
                                            point = geometry,
                                            raster = wind_pollution_data)) %>%
    st_drop_geometry() %>%
    select(firm_code, year, GWRPM25_mean)
}

# Calculate total batches for progress bar
total_batches <- sum(map_dbl(data_firm_wind_pollution_list, nrow)) / 1000
pb <- initialize_progress_bar(total_batches)

results <- list()
counter <- 1

for (element in seq_along(data_firm_wind_pollution_list)) {
  firm_data <- data_firm_wind_pollution_list[[element]]
  wind_data <- data_wind_pollution_list[[element]]
  
  num_batches <- ceiling(nrow(firm_data) / 1000)
  
  for (batch_num in 1:num_batches) {
    pb$tick()
    
    indices <- ((batch_num - 1) * 1000 + 1):(min(batch_num * 1000, nrow(firm_data)))
    batch_result <- process_batch(firm_data[indices, ], wind_data)
    
    results[[counter]] <- batch_result
    counter <- counter + 1
    
    if (counter %% 10 == 0) gc()
  }
}

data_firm_wind_pollution_cone_average <- results %>% list_rbind()
```

Save to RDS file
```{r}
# Save
write_rds(data_firm_wind_pollution_cone_average, file = "./data/data_firm_wind_pollution_cone_average.rds", compress = "gz")
# Restore
data_firm_wind_pollution_cone_average <- read_rds(file = "./data/data_firm_wind_pollution_cone_average.rds")
```

```{r}
rm(data_firm_wind_pollution_cone_average)
gc()
```


## Cone sum
Calculations
```{r}
# Create function
process_batch <- function(batch_data, wind_pollution_data) {
  batch_data %>%
    rowwise() %>%
    mutate(geom_cone = cone_func(point = geometry, angle = wind_dir)) %>%
    ungroup() %>%
    mutate(GWRPM25_mean = cone_sum_func(cone = geom_cone, 
                                            point = geometry,
                                            raster = wind_pollution_data)) %>%
    st_drop_geometry() %>%
    select(firm_code, year, GWRPM25_mean)
}

# Define the batch size
batch_size <- 1000

# Calculate total batches for progress bar
total_batches <- sum(map_dbl(data_firm_wind_pollution_list, nrow)) / batch_size
pb <- initialize_progress_bar(total_batches)

results <- list()
counter <- 1

for (element in seq_along(data_firm_wind_pollution_list)) {
  firm_data <- data_firm_wind_pollution_list[[element]]
  wind_data <- data_wind_pollution_list[[element]]
  
  num_batches <- ceiling(nrow(firm_data) / batch_size)
  
  for (batch_num in 1:num_batches) {
    pb$tick()
    
    indices <- ((batch_num - 1) * batch_size + 1):(min(batch_num * batch_size, nrow(firm_data)))
    batch_result <- process_batch(firm_data[indices, ], wind_data)
    
    results[[counter]] <- batch_result
    counter <- counter + 1
    
    if (counter %% 10 == 0) gc()
  }
}

data_firm_wind_pollution_cone_sum <- results %>% list_rbind()
```

Save to RDS file
```{r}
# Save
write_rds(data_firm_wind_pollution_cone_sum, file = "./data/data_firm_wind_pollution_cone_sum.rds", compress = "gz")
# Restore
data_firm_wind_pollution_cone_sum <- read_rds(file = "./data/data_firm_wind_pollution_cone_sum.rds")
```

```{r}
rm(data_firm_wind_pollution_cone_sum)
gc()
```


## Cone weighted average with windspeed
Calculations
```{r}
# Create function
process_batch <- function(batch_data, wind_pollution_data) {
  # Find median overall windspeed
    median_wind_speed <- terra::values(data_wind_pollution$wind_speed) %>%
      median(na.rm = TRUE)
  
  batch_data %>%
    rowwise() %>%
    mutate(geom_cone = cone_func(point = geometry, angle = wind_dir,
                                 distance = if_else(wind_speed > median_wind_speed,
                                                    25000, 10000))) %>%
    ungroup() %>%
    mutate(GWRPM25_mean = cone_average_func(cone = geom_cone, 
                                            point = geometry,
                                            raster = wind_pollution_data)) %>%
    st_drop_geometry() %>%
    select(firm_code, year, GWRPM25_mean)
}

# Define the batch size
batch_size <- 1000

# Calculate total batches for progress bar
total_batches <- sum(map_dbl(data_firm_wind_pollution_list, nrow)) / batch_size
pb <- initialize_progress_bar(total_batches)

results <- list()
counter <- 1

for (element in seq_along(data_firm_wind_pollution_list)) {
  firm_data <- data_firm_wind_pollution_list[[element]]
  wind_data <- data_wind_pollution_list[[element]]
  
  num_batches <- ceiling(nrow(firm_data) / batch_size)
  
  for (batch_num in 1:num_batches) {
    pb$tick()
    
    indices <- ((batch_num - 1) * batch_size + 1):(min(batch_num * batch_size, nrow(firm_data)))
    batch_result <- process_batch(firm_data[indices, ], wind_data)
    
    results[[counter]] <- batch_result
    counter <- counter + 1
    
    if (counter %% 10 == 0) gc()
  }
}

data_firm_wind_pollution_cone_average_windspeed <- results %>% list_rbind()
```

Saving to RDS file
```{r}
# Save
write_rds(data_firm_wind_pollution_cone_average_windspeed, file = "./data/data_firm_wind_pollution_cone_average_windspeed.rds", compress = "gz")
# Restore
data_firm_wind_pollution_cone_average_windspeed <- read_rds("./data/data_firm_wind_pollution_cone_average_windspeed.rds")
```

```{r}
rm(data_firm_wind_pollution_cone_average_windspeed)
gc()
```


## Cone sum with windspeed
Calculations
```{r}
# Create function
process_batch <- function(batch_data, wind_pollution_data) {
  # Find median overall windspeed
    median_wind_speed <- terra::values(data_wind_pollution$wind_speed) %>%
      median(na.rm = TRUE)
  
  batch_data %>%
    rowwise() %>%
    mutate(geom_cone = cone_func(point = geometry, angle = wind_dir,
                                 distance = if_else(wind_speed > median_wind_speed,
                                                    25000, 10000))) %>%
    ungroup() %>%
    mutate(GWRPM25_mean = cone_sum_func(cone = geom_cone, 
                                            point = geometry,
                                            raster = wind_pollution_data)) %>%
    st_drop_geometry() %>%
    select(firm_code, year, GWRPM25_mean)
}

# Define the batch size
batch_size <- 1000

# Calculate total batches for progress bar
total_batches <- sum(map_dbl(data_firm_wind_pollution_list, nrow)) / batch_size
pb <- initialize_progress_bar(total_batches)

results <- list()
counter <- 1

for (element in seq_along(data_firm_wind_pollution_list)) {
  firm_data <- data_firm_wind_pollution_list[[element]]
  wind_data <- data_wind_pollution_list[[element]]
  
  num_batches <- ceiling(nrow(firm_data) / batch_size)
  
  for (batch_num in 1:num_batches) {
    pb$tick()
    
    indices <- ((batch_num - 1) * batch_size + 1):(min(batch_num * batch_size, nrow(firm_data)))
    batch_result <- process_batch(firm_data[indices, ], wind_data)
    
    results[[counter]] <- batch_result
    counter <- counter + 1
    
    if (counter %% 10 == 0) gc()
  }
}

data_firm_wind_pollution_cone_sum_windspeed <- results %>% list_rbind()
```

Save to RDS file
```{r}
# Save
write_rds(data_firm_wind_pollution_cone_sum_windspeed, file = "./data/data_firm_wind_pollution_cone_sum_windspeed.rds", compress = "gz")
# Restore
data_firm_wind_pollution_cone_sum_windspeed <- read_rds(file = "./data/data_firm_wind_pollution_cone_sum_windspeed.rds")
```

```{r}
rm(data_firm_wind_pollution_cone_sum_windspeed)
gc()
```


# Combining to one object
firm_code and all pollution values 1 to 6
```{r}
# Import data from .rds files
data_firm_wind_pollution_no_geom <- read_rds("./data/data_firm_wind_pollution.rds") %>%
  st_drop_geometry() %>%
  select(firm_code, year, wind_speed, wind_dir, GWRPM25)

data_firm_wind_pollution_surrounding <- read_rds("./data/data_firm_wind_pollution_surrounding.rds")
data_firm_wind_pollution_cone_average <- read_rds("./data/data_firm_wind_pollution_cone_average.rds") %>%
  rename(GWRPM25_cone_mean = GWRPM25_mean)
data_firm_wind_pollution_cone_sum <- read_rds("./data/data_firm_wind_pollution_cone_sum.rds") %>%
  rename(GWRPM25_cone_sum = GWRPM25_sum)
data_firm_wind_pollution_cone_average_windspeed <- read_rds("./data/data_firm_wind_pollution_cone_average_windspeed.rds") %>%
  rename(GWRPM25_cone_windspeed_mean = GWRPM25_mean)
data_firm_wind_pollution_cone_sum_windspeed <- read_rds("./data/data_firm_wind_pollution_cone_sum_windspeed.rds") %>%
  rename(GWRPM25_cone_windspeed_sum = GWRPM25_sum)

# Because I dont use joins but just add the columns, the order of firm_code and year is important
identical(data_firm_wind_pollution_no_geom$firm_code, data_firm_wind_pollution_surrounding$firm_code)
identical(data_firm_wind_pollution_no_geom$firm_code, data_firm_wind_pollution_cone_average$firm_code)
identical(data_firm_wind_pollution_no_geom$firm_code, data_firm_wind_pollution_cone_sum$firm_code)
identical(data_firm_wind_pollution_no_geom$firm_code, data_firm_wind_pollution_cone_average_windspeed$firm_code)
identical(data_firm_wind_pollution_no_geom$firm_code, data_firm_wind_pollution_cone_sum_windspeed$firm_code)

# Combining all data
data_firm_wind_pollution_combined <- data_firm_wind_pollution_no_geom %>%
  mutate(GWRPM25_surrounding_mean = data_firm_wind_pollution_surrounding$GWRPM25_surrounding_mean,
         GWRPM25_surrounding_sum = data_firm_wind_pollution_surrounding$GWRPM25_surrounding_sum,
         GWRPM25_cone_mean = data_firm_wind_pollution_cone_average$GWRPM25_cone_mean,
         GWRPM25_cone_sum = data_firm_wind_pollution_cone_sum$GWRPM25_cone_sum,
         GWRPM25_cone_windspeed_mean = data_firm_wind_pollution_cone_average_windspeed$GWRPM25_cone_windspeed_mean,
         GWRPM25_cone_windspeed_sum = data_firm_wind_pollution_cone_sum_windspeed$GWRPM25_cone_windspeed_sum)

data_firm_wind_pollution_combined
```

Write combined data to .rds and .csv
```{r}
# Save
write_rds(data_firm_wind_pollution_combined, "./data/data_firm_wind_pollution_combined.rds", compress = "gz")
write_csv(data_firm_wind_pollution_combined, "./data/data_firm_wind_pollution_combined.csv.gz")

# Restore
data_firm_wind_pollution_combined <- read_rds("./data/data_firm_wind_pollution_combined.rds")
```

