---
title: "China Wind Data"
author: "Sebastian Geis"
date: "2024-01-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE}
library(progress)
library(units)
library(rvest)
library(httr)

library(metR)
library(raster)
library(terra)
library(sf)
library(stars)
library(ggspatial)
library(gstat)

library(tidyverse)
library(lubridate)
library(vroom)
#library(furrr)
```

# Get list of stations in China
Station list from [NOAA](https://www.ncei.noaa.gov/pub/data/noaa/isd-history.csv)

Specification:
```
 USAF = Air Force station ID. May contain a letter in the first position.
 WBAN = NCDC WBAN number
 CTRY = FIPS country ID
   ST = State for US stations
 ICAO = ICAO ID
  LAT = Latitude in thousandths of decimal degrees
  LON = Longitude in thousandths of decimal degrees
 ELEV = Elevation in meters
BEGIN = Beginning Period Of Record (YYYYMMDD). There may be reporting gaps within the P.O.R.
  END = Ending Period Of Record (YYYYMMDD). There may be reporting gaps within the P.O.R.
```

```{r}
download.file(url = "https://www.ncei.noaa.gov/pub/data/noaa/isd-history.csv", destfile = "./data/isd-history.csv", method = "curl")

stations_isd_full <- read_csv("./data/isd-history.csv") %>%
  janitor::clean_names()

stations_isd_full_china <- stations_isd_full %>%
  filter(ctry == "CH") %>%
  pull(usaf)
```

Keep only station ids that are found in in the [isd lite dataset](https://www.ncei.noaa.gov/pub/data/noaa/isd-lite/) for every year from 1989 to 1999
```{r eval=FALSE}
links <- character()

for(year in 1989:1999){
  print(year)
  
  url <- paste0("https://www.ncei.noaa.gov/pub/data/noaa/isd-lite/", year, "/")
  
  html <- GET(url) %>% content("text") %>% read_html()
  
  links_new <- html %>% 
    html_nodes("a") %>%
    html_attr("href") %>%
  # Filter out links that end with .gz
    .[grepl("\\.gz$", .)]
  
  links <- append(links, links_new)
}

remaining_stations <- links %>%
  tibble() %>%
  rename(full_name = 1) %>%
  mutate(id = str_extract(full_name, "^\\d{6}"),
         year = str_extract(full_name, "(\\d{4})\\.gz$", group = 1)) %>%
  select(-full_name) %>%
  group_by(id) %>%
  count() %>%
  filter(n == 11,
         id %in% stations_isd_full_china) %>%
  pull(id)

length(remaining_stations)
```

Get location of stations
```{r}
stations_location <- stations_isd_full %>%
  select(id = usaf, lat, lon) %>%
  filter(id %in% remaining_stations) %>%
  st_as_sf(coords = c("lon", "lat"), crs = 4326)
```

# Download data
I use the [ISD lite data](https://www.ncei.noaa.gov/pub/data/noaa/isd-lite/), which is smaller but still contains wind speed and direction.

Download using loop
```{r warning=FALSE, eval=FALSE}
base_url_isd_lite <- "https://www.ncei.noaa.gov/pub/data/noaa/isd-lite/"

years <- 1989:1999
#years <- 1990

dir.create("./data/data_isd_lite", showWarnings = FALSE)

for(year in years){
  print(year)
  
  for (station in remaining_stations) {
    file_name <- paste0(station, "-99999-", year, ".gz")
    file_url <- paste0(base_url_isd_lite, year, "/", file_name)
    output_file <- paste0("./data/data_isd_lite/", year, "_", file_name)
    
    sink("/dev/null")
    try(download.file(file_url, output_file, method = "auto", quiet = TRUE, mode = "wb"))
    sink()
  }
}
```

Download with `curl::multi_download()`.
Is MUCH faster, but in the end a few files are missing.
```{r eval=FALSE}
base_url_isd_lite <- "https://www.ncei.noaa.gov/pub/data/noaa/isd-lite/"
years <- 1989:1999

dir.create("data_isd_lite", showWarnings = FALSE)

# Create vector of all URLs and resulting filenames
urls <- character()
output_files <- character()

for(year in years){
  for (station in remaining_stations) {
    file_name <- paste0(station, "-99999-", year, ".gz")
    urls <- append(urls, paste0(base_url_isd_lite, year, "/", file_name))
    output_files <- append(output_files, paste0("./data/data_isd_lite/", year, "_", file_name))
  }
}

# Download files
curl::multi_download(urls = urls, destfiles = output_files, progress = TRUE)
```

**Now unzip all files manually**, with MacOS or Linux use `gunzip *.gz` in the data directory.
Reading in all files and combining them, then writing them back as one file
```{r}
# List all the files in the "data_isd_lite" folder
files <- list.files("./data/data_isd_lite", pattern = "\\d{4}$", full.names = TRUE)

# Define the column types for the columns
positions <- fwf_cols(year = c(1,4), month = c(6,7), day = c(9,11), hour = c(12,13), temp = c(14,19), dew = c(20,24), pres = c(26,31), wind_dir = c(32,37), wind_speed = c(38,43))

types <- cols("i", "i", "i", "i", "i", "i", "i", "i", "i")
                      

# Read and combine the files into a single data frame
data_isd_lite_combined <- bind_rows(lapply(files, function(file) {
  readr::read_fwf(file, col_positions = positions,
         col_types = types) %>%
    mutate(id = str_extract(file, "data_isd_lite\\/\\d{4}_(\\d+)-\\d+-\\d{4}", group = 1)) %>%
    mutate(date = ymd_h(paste(year, month, day, hour)), .keep = "unused") %>%
    select(id, date, wind_dir, wind_speed)
}))

write_csv(data_isd_lite_combined, "./data/data_isd_lite_combined.csv")
```

```{r}
data_isd_lite_combined <- read_csv("./data/data_isd_lite_combined.csv")

data_isd_lite_combined
```


# Data preparation
Find average wind direction
```{r}
# Define a function to compute the mean wind direction
mean_wind_direction <- function(wind_directions) {
  wind_directions_rad <- (pi / 180) * wind_directions
  mean_sin <- mean(sin(wind_directions_rad))
  mean_cos <- mean(cos(wind_directions_rad))
  avg_wind_direction_rad <- atan2(mean_sin, mean_cos)
  avg_wind_direction <- (180 / pi) * avg_wind_direction_rad
  if (avg_wind_direction < 0) {
    avg_wind_direction <- avg_wind_direction + 360
  }
  return(avg_wind_direction)
}

# Calculate the average wind direction over whole period by station
# Cut out observations that are far away from china
data_isd_lite_mean <- data_isd_lite_combined %>%
  filter(wind_dir != -9999, wind_speed != -9999) %>%
  group_by(id) %>%
  summarise(avg_wind_dir = mean_wind_direction(wind_dir), 
            avg_wind_speed = mean(wind_speed)) %>%
  left_join(stations_location, by = join_by(id)) %>%
  st_as_sf() %>%
  st_filter(china_border %>% st_buffer(dist = 100000))
```

Saving / Reading 'data_isd_lite_mean'
```{r}
#st_write(data_isd_lite_mean, "./data/data_isd_lite_mean.gpkg", append = FALSE)

data_isd_lite_mean <- st_read("./data/data_isd_lite_mean.gpkg")

data_isd_lite_mean
```

Simple Plotting
```{r}
china_border <- giscoR::gisco_get_countries(country = "CN")

ggplot()+
  geom_sf(data = china_border)+
  geom_sf(data = data_isd_lite_mean)+
  theme_bw()+
  labs(x = "lon", y = "lat")
```

Plotting with wind speed and direction
```{r}
ggplot() +
  geom_sf(data = china_border) +
  geom_sf(data = data_isd_lite_mean, aes(color = avg_wind_speed), size = 1) +
  metR::geom_arrow(data = data_isd_lite_mean %>% filter(avg_wind_speed < 150), 
                   aes(x = st_coordinates(geom)[, 1], 
                       y = st_coordinates(geom)[, 2], 
                       #mag = avg_wind_speed, 
                       mag = 1,
                       angle = avg_wind_dir, 
                       color = avg_wind_speed),
                   arrow.length = 0.3,
                   arrow.type = "open",
                   pivot = 0,
                   direction = 2,
                   start = 90+180) +
  coord_sf()+
  scale_color_viridis_c(option = "plasma")+
  scale_mag(max_size = .5)+
  theme_bw()+
  labs(x = "lon", 
       y = "lat",
       color = "Average\nWind\nSpeed")+
  guides(mag = FALSE)

#ggsave("./plots/plot_raw_windspeed.pdf", width = 10, height = 6)
```

To check if plotted direction is correct with an example plot and custom wind direction.
```{r}
data_isd_lite_mean %>% slice_head(n = 1) %>% 
  mutate(avg_wind_dir = 45) %>%
  ggplot()+
  geom_sf()+
  metR::geom_arrow(aes(x = st_coordinates(geom)[, 1], 
                       y = st_coordinates(geom)[, 2], 
                       mag = .5, 
                       angle = avg_wind_dir, 
                       color = avg_wind_speed),
                   arrow.type = "open",
                   pivot = 0,
                   direction = 2,
                   start = 90+180)
```

# Interpolation
Reading in .nc file. FILE IS MISSING NOW.
```{r eval=FALSE}
#nc_data <- raster::brick("V5GL02.HybridPM25.China.200001-200012.nc")
#nc_data

#plot(nc_data)
```

datum=WGS84
extent     : 73, 140, 18, 54  (xmin, xmax, ymin, ymax)
resolution : 0.01, 0.01  (x, y)

Create grid
```{r}
# Set grid parameters
xmin <- 73
xmax <- 140
ymin <- 18
ymax <- 54
xres <- 0.01
yres <- 0.01

# Create grid
# Need a larger grid for cropping china and interpolation
grid_large <- raster(xmn = xmin, xmx = xmax, ymn = ymin, ymx = ymax, res = c(xres*10, yres*10), crs = "+proj=longlat +datum=WGS84 +no_defs")
grid <- raster(xmn = xmin, xmx = xmax, ymn = ymin, ymx = ymax, res = c(xres, yres), crs = "+proj=longlat +datum=WGS84 +no_defs")

# Set random values to grid
# For some reason, without this the st_crop does not work
values(grid_large) <- runif(n = length(grid_large), min = 0, max = 1)
values(grid) <- runif(n = length(grid), min = 0, max = 1)

# Convert terra grid to stars grid,
# Only keep cells that are within Chinas borders
grid_large_stars <- grid_large %>% st_as_stars %>%
  st_crop(china_border %>% st_simplify(dTolerance = 10000))

#plot(grid_large_stars)
```

Using fitting model from gstat library, creating interpolation for wind speed
```{r}
# Fit model
v <- variogram(avg_wind_speed~1, data_isd_lite_mean)
v.m <- fit.variogram(v, vgm(50, "Gau", 500, 10))

plot(v, v.m, plot.numbers = TRUE)

# Interpolation
k <- krige(avg_wind_speed~1, data_isd_lite_mean, grid_large_stars, v.m) %>%
  select(wind_speed = var1.pred)

# Plotting
ggplot() + 
  geom_stars(data = k, aes(fill = wind_speed, x = x, y = y)) + 
  xlab(NULL) + ylab(NULL) +
  geom_sf(data = china_border, fill = NA) + 
  geom_sf(data = data_isd_lite_mean, size = 1)+
  theme_bw()+
  scale_fill_viridis_c(na.value = "transparent")+
  labs(fill = "Average\nWindspeed")

#ggsave("./plots/plot_kriging_windspeed.pdf", width = 10, height = 6)
```

## Wind direction
Example for calculating wind directions
```{r}
# set example
degree <- 45

# convert to coordinates
degree_rad <- degree * pi/180

x <- cos(degree_rad)
y <- sin(degree_rad)

round(x, 2)
round(y, 2)

# convert back to degree
theta_degrees <- atan2(y, x) * 180/pi

# Adjust to ensure the angle is positive
if (theta_degrees < 0) {
  theta_degrees <- theta_degrees + 360
}

theta_degrees
```

Annotation: Wind direction of 0° means the wind is blowing from North.
```{r}
# 1. Convert wind direction to rad and coordinates
data_isd_lite_mean_coords <- data_isd_lite_mean %>%
  mutate(avg_wind_dir_rad = avg_wind_dir * pi/180,
         avg_wind_dir_x = cos(avg_wind_dir_rad),
         avg_wind_dir_y = sin(avg_wind_dir_rad))

# 2. Interpolate X and Y components separately
# Fit model for x
v_x <- variogram(avg_wind_dir_x~1, data_isd_lite_mean_coords)
v.m_x <- fit.variogram(v_x, vgm(1, "Exp", 500, 1))
k_x <- krige(avg_wind_dir_x~1, data_isd_lite_mean_coords, grid_large_stars, v.m_x) %>%
  select(pred_x = var1.pred)

# Fit model for y
v_y <- variogram(avg_wind_dir_y~1, data_isd_lite_mean_coords)
v.m_y <- fit.variogram(v_y, vgm(1, "Exp", 500, 1))
k_y <- krige(avg_wind_dir_y~1, data_isd_lite_mean_coords, grid_large_stars, v.m_y) %>%
  select(pred_y = var1.pred)

# 3. Combine models and calculate degrees
grid_large_final <- c(k, k_x, k_y) %>%
  mutate(wind_dir = atan2(pred_y, pred_x) * 180/pi,
         wind_dir = if_else(wind_dir < 0, wind_dir + 360, wind_dir))
grid_large_final
```

```{r}
set.seed(1)

sample <- grid_large_final %>% rast() %>%
  spatSample(size = 2000, xy = TRUE) %>%
  drop_na() %>%
  st_as_sf(coords = c("x", "y"), crs = 4326)

ggplot() +
  geom_sf(data = china_border) +
  geom_sf(data = sample, aes(color = wind_speed_wind_speed), size = 1) +
  metR::geom_arrow(data = sample %>% filter(wind_speed_wind_speed < 150), 
                   aes(x = st_coordinates(geometry)[, 1], 
                       y = st_coordinates(geometry)[, 2], 
                       #mag = avg_wind_speed, 
                       mag = 1,
                       angle = wind_dir_wind_dir, 
                       color = wind_speed_wind_speed),
                   arrow.length = 0.3,
                   arrow.type = "open",
                   pivot = 0,
                   direction = 2,
                   start = 90+180) +
  coord_sf()+
  scale_color_viridis_c(option = "plasma")+
  scale_mag(max_size = .5)+
  theme_bw()+
  labs(x = "lon", 
       y = "lat",
       color = "Average\nWind\nSpeed")+
  guides(mag = FALSE)

#ggsave("./plots/plot_windspeed_after_interpolation.jpg")
```

# Save raster
Convert back to terra and split raster 1:10 to get desired resolution (as grid_small)
```{r}
grid_small_final <- grid_large_final %>% select(wind_speed, wind_dir) %>% rast() %>% disagg(fact=c(10, 10))
names(grid_small_final) <- c("wind_speed", "wind_dir")

plot(grid_small_final)

#plot(grid_small_k_windspeed$var1.pred_var1.pred)
```

Write to NetCDF and load again
```{r}
#writeCDF(grid_small_final, "./data/grid_small_final.nc", overwrite = TRUE, compression = 7)

grid_small_final <- terra::rast("./data/grid_small_final.nc")
names(grid_small_final) <- c("wind_speed", "wind_dir")
```